Adaptive Distance Metric Selection for Supervised Classification

### 2016-09-28 latex/Adaptive_distance_metric_notes.tex
Add

@@

Model \eqref{model:1} can be expressed as a huge mixed-integer linear programming problem:
\begin{subequations} \label{model:milp_with_outlier_detection}
\begin{alignat}{4}
\max_{\lambda,\v{B},\v{d},\v{w},\v{y}}~~& f(\vlambda) = \sum_{i \in \mc{N}} f_i(\lambda_i) = \sum_{i \in \mc{N}} (\lambda_i - \rho z_i) & & \\
\st~~& \sum_{j \in \mc{C}_i} w_{ij} + \lambda_i \leq d_{ik} + M_i z_i  && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \\
    & \lambda_i \leq 1 - z_i && \qquad \forall i \in \mc{N} \label{eq:outlier_separation_logic} \\
    & w_{ij} \leq d_{ij} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_1} \\
    & w_{ij} \leq y_{ij} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_2} \\
    & w_{ij} \geq d_{ij} + y_{ij} - 1 && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_3} \\
    & \sum_{j \in \mc{C}_i} y_{ij} = 1 && \qquad \forall i \in \mc{N} \\
    & d_{ij} = \sum_{k=1}^p \delta_{ijk}^2 b_{kk} + 2 \sum_{k=1}^{p-1} \sum_{\ell=k+1}^p  \delta_{ijk} \delta_{ij\ell} b_{k\ell} && \qquad \forall i,j \in \mc{N} \label{eq:big_milp_distance_def_constr} \\
    & b_{k\ell} \in \Re && \qquad \forall k=1,\dots,p, \ell=k,\dots,p \\
    & d_{ij} \geq 0 && \qquad \forall i,j \in \mc{N} \\
    & w_{ij} \geq 0 && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \\
    & y_{ij} \in \{0,1\} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \\
    & z_{i} \in \{0,1\} && \qquad \forall i \in \mc{N} \\
    & \lambda_i \geq 0 & & \qquad \forall i \in \mc{N}
\end{alignat}
\end{subequations}

@@

>>>>

\usepackage[colorinlistoftodos,bordercolor=orange,backgroundcolor=orange!20,linecolor=orange,textsize=scriptsize]{todonotes}

@@

Model \eqref{model:1} can be expressed as a huge mixed-integer linear programming problem:
\begin{subequations} \label{model:milp_with_outlier_detection}
\begin{alignat}{4}
\max_{\lambda,\v{B},\v{d},\v{w},\v{y}}~~& f(\vlambda) = \sum_{i \in \mc{N}} f_i(\lambda_i) = \sum_{i \in \mc{N}} (\lambda_i - \rho z_i) & & \\
\st~~& \sum_{j \in \mc{C}_i} w_{ij} + \lambda_i \leq d_{ik} + M_i z_i  && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \\
    & \lambda_i \leq 1 - z_i && \qquad \forall i \in \mc{N} \label{eq:outlier_separation_logic} \\
    & w_{ij} \leq d_{ij} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_1} \\
    & w_{ij} \leq y_{ij} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_2} \\
    & w_{ij} \geq d_{ij} + y_{ij} - 1 && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_3} \\
    & \sum_{j \in \mc{C}_i} y_{ij} = 1 && \qquad \forall i \in \mc{N} \\
    & d_{ij} = \sum_{k=1}^p \delta_{ijk}^2 b_{kk} + 2 \sum_{k=1}^{p-1} \sum_{\ell=k+1}^p  \delta_{ijk} \delta_{ij\ell} b_{k\ell} && \qquad \forall i,j \in \mc{N} \label{eq:big_milp_distance_def_constr} \\
    & b_{k\ell} \in \Re && \qquad \forall k=1,\dots,p, \ell=k,\dots,p \\
    & d_{ij} \geq 0 && \qquad \forall i,j \in \mc{N} \\
    & w_{ij} \geq 0 && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \\
    & y_{ij} \in \{0,1\} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \\
    & z_{i} \in \{0,1\} && \qquad \forall i \in \mc{N} \\
    & \lambda_i \geq 0 & & \qquad \forall i \in \mc{N}
\end{alignat}
\end{subequations}
\todo[inline]{
Are we missing $a$ in   \eqref{eq:big_milp_distance_def_constr}
}

@@

\subsection{New Idea}

put here the model from above using only one  $\lambda$

\begin{subequations} \label{model:milp_with_outlier_detection_adssasdsa}
\begin{alignat}{4}
\max_{\lambda,\v{B},\v{d},\v{w},\v{y}}~~& f(\vlambda) = \sum_{i \in \mc{N}} f_i(\lambda_i) = \sum_{i \in \mc{N}} (\lambda_i - \rho z_i) & & \\
\st~~& \sum_{j \in \mc{C}_i} w_{ij} + \lambda_i \leq d_{ik} + M_i z_i  && \qquad \forall i \in \mc{N}, k \in \mc{N}\backslash\mc{C}_i \\
    & \lambda_i \leq 1 - z_i && \qquad \forall i \in \mc{N} \label{eq:outlier_separation_logic_adssasdsa} \\
    & w_{ij} \leq d_{ij} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_1_adssasdsa} \\
    & w_{ij} \leq y_{ij} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_2_adssasdsa} \\
    & w_{ij} \geq d_{ij} + y_{ij} - 1 && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \label{eq:mccormick_3_adssasdsa} \\
    & \sum_{j \in \mc{C}_i} y_{ij} = 1 && \qquad \forall i \in \mc{N} \\
    & d_{ij} = \sum_{k=1}^p \delta_{ijk}^2 b_{kk} + 2 \sum_{k=1}^{p-1} \sum_{\ell=k+1}^p  \delta_{ijk} \delta_{ij\ell} b_{k\ell} && \qquad \forall i,j \in \mc{N} \label{eq:big_milp_distance_def_constr_adssasdsa} \\
    & b_{k\ell} \in \Re && \qquad \forall k=1,\dots,p, \ell=k,\dots,p \\
    & d_{ij} \geq 0 && \qquad \forall i,j \in \mc{N} \\
    & w_{ij} \geq 0 && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \\
    & y_{ij} \in \{0,1\} && \qquad \forall i \in \mc{N}, i \in \mc{C}_i \\
    & z_{i} \in \{0,1\} && \qquad \forall i \in \mc{N} \\
    & \lambda_i \geq 0 & & \qquad \forall i \in \mc{N}
\end{alignat}
\end{subequations}
